---
title: "RNA-Seq Downstream Analysis Report"
author: '<div class="team-date-box"><p>CCRSF-IFX Team</p></div>'
date: '<div class="team-date-box"><p>`r Sys.Date()`</p></div>'
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    df_print: paged
    css: styles.css
params:
  config_path: NULL
runtime: shiny
---
```{r setup, include=FALSE}
# Load necessary libraries
library(yaml)
library(DT)
library(knitr)
library(ggplot2)
library(plotly)
library(png)
library(grid)
library(shiny)

# Use the parameter for the configuration path, default to "../../config/config.yaml" if NULL
config_path <- if (!is.null(params$config_path)) {
  params$config_path
} else {
  "../../config/config.yaml"
}

# Read the configuration file using the path from params
cat("Loading configuration from:", config_path, "\n")
config <- yaml::read_yaml(config_path)

results_dir <- config$results
cat("Results directory:", results_dir, "\n")

# Function to check if a file is a valid PNG
is_valid_png <- function(file_path) {
  if (!file.exists(file_path)) {
    return(FALSE)
  }
  con <- file(file_path, "rb")
  magic_number <- readBin(con, "raw", n = 8)
  close(con)
  identical(magic_number, as.raw(c(0x89, 0x50, 0x4E, 0x47, 0x0D, 0x0A, 0x1A, 0x0A)))
}
## Library Distribution

```{r library_distribution, echo=FALSE, results='asis'}
cat("## Library Distribution\n")

# Library Distribution Plot
cat("<details><summary>Click to expand Library Distribution Plot</summary>\n")
libdistrib_file <- file.path(results_dir, "libdistrib_mqc.png")

if (is_valid_png(libdistrib_file)) {
  shiny::tabsetPanel(
    shiny::tabPanel(
      title = "Library Distribution",
      div(
        img(src = libdistrib_file, width = "100%"),
        p("Plot: libdistrib_mqc.png")
      )
    )
  )
} else {
  cat("Library distribution plot file not found or is not a valid PNG format.\n")
}
cat("</details>\n\n")

## DESeq2 Analysis Results

```{r deseq2_analysis, echo=FALSE, results='asis'}
cat("## DESeq2 Analysis Results\n")
# DESeq2 Normalized Histogram
cat("<details><summary>Click to expand DESeq2 Normalized Histogram</summary>\n")
hist_file <- file.path(results_dir, "HistDesq2normFilter_mqc.png")

if (is_valid_png(hist_file)) {
  shiny::tabsetPanel(
    shiny::tabPanel(
      title = "Normalized Histogram",
      div(
        img(src = hist_file, width = "100%"),
        p("Plot: HistDesq2normFilter_mqc.png")
      )
    )
  )
} else {
  cat("DESeq2 normalized histogram plot file not found or is not a valid PNG format.\n")
}
cat("</details>\n\n")
# DESeq2 MA Plots (Exclude those with "limma" in the name)
cat("<details><summary>Click to expand DESeq2 MA Plots</summary>\n")
ma_files <- list.files(results_dir, pattern = "MAplot_.*_mqc\\.png$")
ma_files <- ma_files[!grepl("limma", ma_files)]  # Exclude files containing "limma"

if (length(ma_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(ma_files)) {
    file_path <- file.path(results_dir, ma_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("MA Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", ma_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "DESeq2MAPlots", tab_panels))
  } else {
    cat("No valid DESeq2 MA plot files found.\n")
  }
} else {
  cat("No DESeq2 MA plot files found.\n")
}
cat("</details>\n\n")

# DESeq2 Heatmaps (Exclude those with "limma" in the name)
cat("<details><summary>Click to expand DESeq2 Heatmaps</summary>\n")
heatmap_files <- list.files(results_dir, pattern = "heatmap_.*_mqc\\.png$")
heatmap_files <- heatmap_files[!grepl("limma", heatmap_files)]  # Exclude files containing "limma"

if (length(heatmap_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(heatmap_files)) {
    file_path <- file.path(results_dir, heatmap_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Heatmap", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", heatmap_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "DESeq2Heatmaps", tab_panels))
  } else {
    cat("No valid DESeq2 heatmap files found.\n")
  }
} else {
  cat("No DESeq2 heatmap files found.\n")
}
cat("</details>\n\n")
## EdgeR Analysis Results

```{r edger_analysis, echo=FALSE, results='asis'}
cat("## EdgeR Analysis Results\n")
# EdgeR Normalized Histogram
cat("<details><summary>Click to expand EdgeR Normalized Histogram</summary>\n")
hist_file <- file.path(results_dir, "HistEdgeRnormFilter_mqc.png")

if (is_valid_png(hist_file)) {
  shiny::tabsetPanel(
    shiny::tabPanel(
      title = "Normalized Histogram",
      div(
        img(src = hist_file, width = "100%"),
        p("Plot: HistEdgeRnormFilter_mqc.png")
      )
    )
  )
} else {
  cat("EdgeR normalized histogram plot file not found or is not a valid PNG format.\n")
}
cat("</details>\n\n")
# EdgeR MDS BCV Plot
cat("<details><summary>Click to expand MDS BCV Plot</summary>\n")
mds_bcv_file <- file.path(results_dir, "MDS_bcv_mqc.png")

if (is_valid_png(mds_bcv_file)) {
  shiny::tabsetPanel(
    shiny::tabPanel(
      title = "MDS BCV Plot",
      div(
        img(src = mds_bcv_file, width = "100%"),
        p("Plot: MDS_bcv_mqc.png")
      )
    )
  )
} else {
  cat("EdgeR MDS BCV plot file not found or is not a valid PNG format.\n")
}
cat("</details>\n\n")

# EdgeR MDS logFC Plot
cat("<details><summary>Click to expand MDS logFC Plot</summary>\n")
mds_logfc_file <- file.path(results_dir, "MDS_logFC_mqc.png")

if (is_valid_png(mds_logfc_file)) {
  shiny::tabsetPanel(
    shiny::tabPanel(
      title = "MDS logFC Plot",
      div(
        img(src = mds_logfc_file, width = "100%"),
        p("Plot: MDS_logFC_mqc.png")
      )
    )
  )
} else {
  cat("EdgeR MDS logFC plot file not found or is not a valid PNG format.\n")
}
cat("</details>\n\n")

# EdgeR BCV Plot
cat("<details><summary>Click to expand BCV Plot</summary>\n")
bcv_file <- file.path(results_dir, "BCVplot_mqc.png")

if (is_valid_png(bcv_file)) {
  shiny::tabsetPanel(
    shiny::tabPanel(
      title = "BCV Plot",
      div(
        img(src = bcv_file, width = "100%"),
        p("Plot: BCVplot_mqc.png")
      )
    )
  )
} else {
  cat("EdgeR BCV plot file not found or is not a valid PNG format.\n")
}
cat("</details>\n\n")
# EdgeR Smear Plots
cat("<details><summary>Click to expand EdgeR Smear Plots</summary>\n")
smear_files <- list.files(results_dir, pattern = "Smearplot_.*_mqc\\.png$")

if (length(smear_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(smear_files)) {
    file_path <- file.path(results_dir, smear_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Smear Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", smear_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "EdgeRSmearPlots", tab_panels))
  } else {
    cat("No valid EdgeR Smear plot files found.\n")
  }
} else {
  cat("No EdgeR Smear plot files found.\n")
}
cat("</details>\n\n")
# EdgeR Heatmaps
cat("<details><summary>Click to expand EdgeR Heatmaps</summary>\n")
heatmap_files <- list.files(results_dir, pattern = "edgeR_heatmaps_samplebysample_mqc_.*\\.png$")

if (length(heatmap_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(heatmap_files)) {
    file_path <- file.path(results_dir, heatmap_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Heatmap", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", heatmap_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "EdgeRHeatmaps", tab_panels))
  } else {
    cat("No valid EdgeR heatmap files found.\n")
  }
} else {
  cat("No EdgeR heatmap files found.\n")
}
cat("</details>\n\n")

# EdgeR prcomp Plots
cat("<details><summary>Click to expand EdgeR prcomp Plots</summary>\n")
prcomp_files <- list.files(results_dir, pattern = "edgeR_prcomp_mqc_.*\\.png$")

if (length(prcomp_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(prcomp_files)) {
    file_path <- file.path(results_dir, prcomp_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("prcomp Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", prcomp_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "EdgeRPrcompPlots", tab_panels))
  } else {
    cat("No valid EdgeR prcomp plot files found.\n")
  }
} else {
  cat("No EdgeR prcomp plot files found.\n")
}
cat("</details>\n\n")

# EdgeR PCA Plots
cat("<details><summary>Click to expand EdgeR PCA Plots</summary>\n")
pca_files <- list.files(results_dir, pattern = "edgeR_pca_mqc_.*\\.png$")

if (length(pca_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(pca_files)) {
    file_path <- file.path(results_dir, pca_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("PCA Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", pca_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "EdgeRPCAPlots", tab_panels))
  } else {
    cat("No valid EdgeR PCA plot files found.\n")
  }
} else {
  cat("No EdgeR PCA plot files found.\n")
}
cat("</details>\n\n")
## Limma-Voom Analysis Results

```{r limma_voom_analysis, echo=FALSE, results='asis'}
cat("## Limma-Voom Analysis Results\n")

# Limma-Voom MA Plots
cat("<details><summary>Click to expand Limma-Voom MA Plots</summary>\n")
ma_voom_files <- list.files(results_dir, pattern = "MAplot_limma_voom_.*_mqc\\.png$")

if (length(ma_voom_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(ma_voom_files)) {
    file_path <- file.path(results_dir, ma_voom_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("MA Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", ma_voom_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "LimmaVoomMAPlots", tab_panels))
  } else {
    cat("No valid Limma-Voom MA plot files found.\n")
  }
} else {
  cat("No Limma-Voom MA plot files found.\n")
}
cat("</details>\n\n")

# Limma-Voom Heatmaps
cat("<details><summary>Click to expand Limma-Voom Heatmaps</summary>\n")
heatmap_voom_files <- list.files(results_dir, pattern = "heatmap_limma_voom_.*_mqc\\.png$")

if (length(heatmap_voom_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(heatmap_voom_files)) {
    file_path <- file.path(results_dir, heatmap_voom_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Heatmap", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", heatmap_voom_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "LimmaVoomHeatmaps", tab_panels))
  } else {
    cat("No valid Limma-Voom heatmap files found.\n")
  }
} else {
  cat("No Limma-Voom heatmap files found.\n")
}
cat("</details>\n\n")
## Venn Diagrams

```{r venn_diagrams, echo=FALSE, results='asis'}
cat("## Venn Diagrams\n")

# Venn Diagrams
cat("<details><summary>Click to expand Venn Diagrams</summary>\n")
venn_files <- list.files(results_dir, pattern = "venn_diagram_.*_mqc\\.png$")

if (length(venn_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(venn_files)) {
    file_path <- file.path(results_dir, venn_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Venn Diagram", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", venn_files[i]))
        )
      )
    }
  }
  
  # Only create the tabsetPanel if there are valid panels
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "VennDiagrams", tab_panels))
  } else {
    cat("No valid Venn diagram files found.\n")
  }
} else {
  cat("No Venn diagram files found.\n")
}
cat("</details>\n\n")

## Gene Set Enrichment Analysis

```{r Gene_set_Analysis, echo=FALSE, results='asis'}
cat("## Gene Set Enrichment Analysis\n")

# Dot Plots
cat("<details><summary>Click to expand Dot Plots</summary>\n")
dotplot_files <- list.files(results_dir, pattern = "pathway_analysis_.*_dotplot_mqc\\.png$")

if (length(dotplot_files) > 0) {
  # Create a list to store tabPanel objects
  tab_panels <- list()
  
  for (i in seq_along(dotplot_files)) {
    file_path <- file.path(results_dir, dotplot_files[i])
    if (is_valid_png(file_path)) {
      # Append valid tabPanel to the list
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Dot Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", dotplot_files[i]))
        )
      )
    }
  }
  
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "DotPlots", tab_panels))
  } else {
    cat("No valid dot plot files found.\n")
  }
} else {
  cat("No dot plot files found.\n")
}
cat("</details>\n\n")

# Emap Plots
cat("<details><summary>Click to expand Emap Plots</summary>\n")
emapplot_files <- list.files(results_dir, pattern = "pathway_analysis_.*_emapplot_mqc\\.png$")

if (length(emapplot_files) > 0) {
  tab_panels <- list()
  
  for (i in seq_along(emapplot_files)) {
    file_path <- file.path(results_dir, emapplot_files[i])
    if (is_valid_png(file_path)) {
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Emap Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", emapplot_files[i]))
        )
      )
    }
  }
  
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "EmapPlots", tab_panels))
  } else {
    cat("No valid emap plot files found.\n")
  }
} else {
  cat("No emap plot files found.\n")
}
cat("</details>\n\n")

# Cnet Plots
cat("<details><summary>Click to expand Cnet Plots</summary>\n")
cnetplot_files <- list.files(results_dir, pattern = "pathway_analysis_.*_cnetplot_mqc\\.png$")

if (length(cnetplot_files) > 0) {
  tab_panels <- list()
  
  for (i in seq_along(cnetplot_files)) {
    file_path <- file.path(results_dir, cnetplot_files[i])
    if (is_valid_png(file_path)) {
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Cnet Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", cnetplot_files[i]))
        )
      )
    }
  }
  
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "CnetPlots", tab_panels))
  } else {
    cat("No valid cnet plot files found.\n")
  }
} else {
  cat("No cnet plot files found.\n")
}
cat("</details>\n\n")

# Ridge Plots
cat("<details><summary>Click to expand Ridge Plots</summary>\n")
ridgeplot_files <- list.files(results_dir, pattern = "pathway_analysis_.*_ridgeplot_mqc\\.png$")

if (length(ridgeplot_files) > 0) {
  tab_panels <- list()
  
  for (i in seq_along(ridgeplot_files)) {
    file_path <- file.path(results_dir, ridgeplot_files[i])
    if (is_valid_png(file_path)) {
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("Ridge Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", ridgeplot_files[i]))
        )
      )
    }
  }
  
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "RidgePlots", tab_panels))
  } else {
    cat("No valid ridge plot files found.\n")
  }
} else {
  cat("No ridge plot files found.\n")
}
cat("</details>\n\n")

# GSEA Plots
cat("<details><summary>Click to expand GSEA Plots</summary>\n")
gseaplot_files <- list.files(results_dir, pattern = "pathway_analysis_.*_gseaplot_mqc\\.png$")

if (length(gseaplot_files) > 0) {
  tab_panels <- list()
  
  for (i in seq_along(gseaplot_files)) {
    file_path <- file.path(results_dir, gseaplot_files[i])
    if (is_valid_png(file_path)) {
      tab_panels[[i]] <- shiny::tabPanel(
        title = paste("GSEA Plot", i),
        div(
          img(src = file_path, width = "100%"),
          p(paste("Plot:", gseaplot_files[i]))
        )
      )
    }
  }
  
  if (length(tab_panels) > 0) {
    do.call(shiny::tabsetPanel, c(id = "GSEAPlots", tab_panels))
  } else {
    cat("No valid GSEA plot files found.\n")
  }
} else {
  cat("No GSEA plot files found.\n")
}
cat("</details>\n\n")

